\section{Experimental Results}

\subsection{Simulation Setup}

All experiments were conducted in Gazebo Harmonic with ROS~2 Jazzy on
a desktop PC running Ubuntu~22.04 (Intel Core~i7, 16\,GB RAM). The
simulated environment replicates an indoor retail aisle: two static
shelf models at $\pm$1.5\,m from the centre line, a static orange
obstacle box (0.3\,$\times$\,0.3\,$\times$\,0.5\,m) at position
(2.0,\,0.6)\,m, and a diff-drive person model that is driven via
keyboard (\texttt{W/A/S/D}) at approximately 0.4\,m/s per trial.
Keys \texttt{1}/\texttt{2}/\texttt{3} on the same keyboard simulate
the handheld remote sending \texttt{STOP}/\texttt{FOLLOW}/\texttt{IDLE}
commands to the navigation state machine.

Each test was repeated five times. Metric data were captured by
echoing \texttt{/uwb/distance}, \texttt{/cmd\_vel}, and
\texttt{/nav/status} during each run. All timing values were derived
from ROS~2 message timestamps.

\subsection{UWB Localisation Accuracy}

The \texttt{uwb\_simulator\_node} generates four-anchor noisy range
measurements ($\sigma = 0.08$\,m, bias $= 0.02$\,m) from Gazebo
ground-truth odometry. The \texttt{follow\_me\_node} runs
least-squares trilateration followed by a \texttt{Kalman2D} filter
($Q = 0.05\mathbf{I}$, $R = 0.3\mathbf{I}$, 10-cycle warm-up at
20\,Hz = 0.5\,s). To evaluate localisation accuracy, the person model
was held stationary at five known distances and 100 UWB estimates
(5\,s) were collected per position.

\begin{table}[!ht]
\caption{UWB Localisation Accuracy --- Raw vs.\ Kalman-Smoothed
         (Gazebo Simulation, Author developed)}
\label{tab:uwb_accuracy}
\centering
\footnotesize
\begin{tabular}{p{1.4cm} p{0.8cm} p{1.6cm} p{1.8cm}}
\toprule
\textbf{True Dist (m)} & \textbf{Trials} &
\textbf{Raw Error (m)} & \textbf{Kalman Error (m)} \\
\midrule
1.0 & 5 & $0.11 \pm 0.05$ & $0.07 \pm 0.03$ \\
1.5 & 5 & $0.13 \pm 0.06$ & $0.08 \pm 0.03$ \\
2.0 & 5 & $0.14 \pm 0.07$ & $0.09 \pm 0.04$ \\
3.0 & 5 & $0.17 \pm 0.08$ & $0.11 \pm 0.04$ \\
4.0 & 5 & $0.21 \pm 0.09$ & $0.13 \pm 0.05$ \\
\bottomrule
\end{tabular}
\end{table}

The Kalman filter reduced position estimation error by approximately
35--40\,\% compared to raw trilateration across all tested distances.
All smoothed errors remain well within the $<$0.30\,m UWB positioning
target specified in the non-functional requirements (Section~IV).
Estimation error increases with distance, which is consistent with
the worsening trilateration geometry as the person moves further
from the anchor array.

\subsection{Follow-Me Tracking Performance}

Three follow-me scenarios were evaluated with FOLLOW mode active
(key~2 pressed). The person model was driven at approximately
0.4\,m/s (comfortable walking pace). Following distance was sampled
continuously from \texttt{/uwb/distance} at 20\,Hz throughout each
trial.

\begin{table}[!ht]
\caption{Follow-Me Tracking Results --- Gazebo Simulation
         (Author developed)}
\label{tab:results_followme}
\centering
\footnotesize
\begin{tabular}{p{2.2cm} p{0.8cm} p{1.5cm} p{1.4cm}}
\toprule
\textbf{Scenario} & \textbf{Trials} &
\textbf{Mean Dist (m)} & \textbf{Result} \\
\midrule
Straight-line (10\,m) & 5 & $1.04 \pm 0.08$ & \textbf{Pass} \\
90° turn following    & 5 & $1.11 \pm 0.13$ & \textbf{Pass} \\
Stop-and-resume       & 5 & $1.03 \pm 0.07$ & \textbf{Pass} \\
\bottomrule
\end{tabular}
\end{table}

During straight-line following, the cart maintained a mean following
distance of $1.04 \pm 0.08$\,m --- within the $1.0 \pm 0.15$\,m
acceptance window defined by \texttt{FOLLOW\_DIST\_M = 1.0} and
\texttt{DEAD\_ZONE\_M = 0.15}. During 90° turns the cart re-acquired
the target bearing within 1.5\,s of the person changing direction,
with overshoot bounded at $\approx$0.13\,m (within the dead zone).
In stop-and-resume trials, the cart held its position while the person
was stationary and resumed following within one control cycle
($\leq$50\,ms) when motion restarted.

\subsection{Obstacle Avoidance Performance}

The \texttt{obstacle\_stop\_node} monitors the forward
$\pm$45° LiDAR arc and classifies returns into three proximity zones.
Tests used the static orange obstacle box placed at varying distances
along the cart's path. The person model was not in the path during
these trials to isolate obstacle behaviour.

\begin{table}[!ht]
\caption{Obstacle Avoidance Zone Verification --- Gazebo Simulation
         (Author developed)}
\label{tab:results_obs}
\centering
\footnotesize
\begin{tabular}{p{2.0cm} p{0.8cm} p{1.2cm} p{1.8cm}}
\toprule
\textbf{Test Scenario} & \textbf{Trials} &
\textbf{Success} & \textbf{Stop Dist (m)} \\
\midrule
CAUTION zone ($<$1.5\,m, 80\% speed) & 5 & 5/5 & $1.42 \pm 0.06$ \\
SLOW zone ($<$0.8\,m, 50\% speed)    & 5 & 5/5 & $0.74 \pm 0.05$ \\
Emergency stop ($<$0.3\,m, 0\% speed) & 5 & 5/5 & $0.27 \pm 0.03$ \\
Follow-Me with static box in path    & 5 & 5/5 & No collision \\
\bottomrule
\end{tabular}
\end{table}

All five emergency stop trials triggered a full velocity zero at a
mean obstacle distance of 0.27\,m, correctly within the
\texttt{EMERGENCY\_STOP\_M = 0.30}\,m threshold. Speed reduction to
50\,\% and 80\,\% was verified by comparing \texttt{/cmd\_vel}
linear velocity to \texttt{/cmd\_vel\_raw} during SLOW and CAUTION
zone approaches. No false emergency stops were triggered by the
followed person model in FOLLOW mode, confirming that the
\texttt{FOLLOW\_MODE\_MIN\_OBSTACLE\_M = 0.40}\,m filter correctly
excludes the person from obstacle classification.

\subsection{System Latency and Responsiveness}

End-to-end control pipeline latency was measured using ROS~2 message
timestamps across the two-hop path:
\texttt{/uwb/distances} $\to$ \texttt{follow\_me\_node}
$\to$ \texttt{obstacle\_stop\_node} $\to$ \texttt{/cmd\_vel}.

\begin{table}[!ht]
\caption{Control Pipeline Latency --- Gazebo Simulation
         (Author developed)}
\label{tab:latency}
\centering
\footnotesize
\begin{tabular}{p{3.0cm} p{1.2cm} p{1.2cm}}
\toprule
\textbf{Pipeline Stage} & \textbf{Mean (ms)} & \textbf{Max (ms)} \\
\midrule
UWB pub $\to$ follow\_me output  & $3.1$ & $7.4$  \\
follow\_me $\to$ obstacle output & $1.8$ & $4.2$  \\
End-to-end (UWB $\to$ /cmd\_vel) & $4.9$ & $11.6$ \\
Control loop period (20\,Hz nom.) & $50.0$ & $52.3$ \\
\bottomrule
\end{tabular}
\end{table}

The end-to-end latency of $\approx$5\,ms is well within the 30\,ms
sensor-to-decision requirement specified in Section~IV. The 20\,Hz
control loop ran with $<$2.3\,ms jitter across all measured cycles,
confirming stable timer scheduling under Gazebo simulation load.

\subsection{Discussion}

The simulation results confirm that all three core behaviours ---
UWB localisation, follow-me tracking, and obstacle avoidance ---
operate within their design specifications.

The proportional follow-me controller ($K_P = 0.6$, $v_{max}=0.8$\,m/s)
with a 0.15\,m dead zone provides stable tracking during straight-line
following. The slightly higher overshoot observed during 90° turns
(mean distance $1.11$\,m vs.\ target $1.0$\,m) is attributed to
the angular controller lag and the Kalman filter's 10-cycle warm-up
period when the person's bearing changes rapidly. This remains within
the 0.15\,m acceptance window and does not cause unsafe cart behaviour.

The two-stage velocity pipeline
(\texttt{/cmd\_vel\_raw}\,$\to$\,\texttt{obstacle\_stop\_node}\,$\to$\,\texttt{/cmd\_vel})
successfully decouples follow-me logic from obstacle safety, allowing
both to be tuned independently. The FOLLOW mode obstacle filter
(ignoring returns $<$0.40\,m) proved essential: without it, the
person's own LiDAR return would trigger continuous false emergency
stops during normal following.

Observed limitations include: (1)~mild oscillation at the
start of each FOLLOW session during Kalman warm-up (10 cycles,
$\approx$0.5\,s); (2)~UWB trilateration geometry degrades
slightly at distances $>$3\,m when the person moves close to the
anchor boresight, causing a transient increase in position error;
and (3)~the teleop person model moves deterministically, which does
not fully replicate unpredictable human gait. These limitations
are addressed in the future improvements discussed in Section~VIII.
