\section{Non-Functional Requirements}

Non-functional requirements define the quality standards and operational
constraints the Smart Cart system must meet --- not what it does, but how
well it does it. These requirements directly influence the user experience,
safety, and deployment viability of the system.

\subsection{Performance Requirements}

The system must meet the following performance thresholds to function
safely and usefully in a real retail environment:

\begin{table}[!ht]
\caption{Non-Functional Requirements (Author developed)}
\label{tab:nfr}
\centering
\footnotesize
\begin{tabular}{p{2.0cm} p{1.8cm} p{2.8cm}}
\toprule
\textbf{Requirement} & \textbf{Target Value} & \textbf{Justification} \\
\midrule
Sensor-to-decision latency & $<$30\,ms & Cart must react to obstacles before reaching unsafe proximity at walking speed \\
Emergency stop response time & $<$200\,ms & Heel-impact prevention requires sub-200\,ms full brake from walking speed \\
UWB position update rate & $\geq$50\,Hz & Smooth follow-me requires frequent user position updates \\
Maximum following speed & 0.8\,m/s (unloaded) & Matches average comfortable shopping walking pace \\
Battery operational life & $\geq$3 hours continuous & Must cover a full extended shopping session without recharge \\
System boot-up time & $<$15 seconds & Acceptable wait time at cart collection point \\
Weight measurement accuracy & $\pm$200\,g & Sufficient for triggering load-based speed adjustments reliably \\
\bottomrule
\end{tabular}
\end{table}

\subsection{Safety Requirements}

Safety is the highest priority non-functional requirement. The cart
operates in a shared human environment and must never cause harm. The
following safety requirements are mandatory for deployment:
\begin{itemize}
  \item The cart shall never exceed 1.2\,m/s under any operating condition.
  \item The emergency stop mechanism shall operate via a hardware relay, independent of software --- cutting motor power even if the Raspberry Pi crashes.
  \item The cart shall detect and stop for obstacles lower than 20\,cm from the floor (child feet, bags) using IR sensors.
  \item The system shall prevent motion when basket load exceeds 40\,kg.
  \item If the UWB link to the user remote is lost for more than 3 seconds, the cart shall decelerate to a stop and wait.
  \item The cart shall not operate on slopes greater than 10° without triggering a low-speed safe mode.
  \item All exposed electrical components shall be rated IP42 minimum for indoor retail environments.
\end{itemize}

\subsection{Reliability and Availability}

The Smart Cart is a consumer-facing product deployed in a commercial
setting. Reliability failures have direct business and safety consequences.
\begin{itemize}
  \item Mean Time Between Failures (MTBF): The system shall operate for a minimum of 500 continuous shopping sessions before requiring scheduled maintenance.
  \item The software watchdog timer shall recover from non-critical ROS~2 node crashes within 2 seconds without user intervention.
  \item Battery management shall provide at least 60 seconds of safe operation warning before critical shutdown.
  \item All sensor failures shall be detected within one processing cycle (25\,ms) and trigger a safe-mode response.
\end{itemize}

\subsection{Usability Requirements}

The system must be accessible to all user classes without training,
including elderly shoppers and those unfamiliar with technology.
\begin{itemize}
  \item The entire user interface shall consist of two physical buttons only (Follow and Stop) --- no touchscreen, no app, no setup.
  \item LED status colors shall follow universally recognized conventions: green = safe/active, yellow = caution, red = stop/fault.
  \item The remote shall weigh no more than 80\,g and fit comfortably in one hand.
  \item A new user shall be able to begin using the cart within 30 seconds of receiving the remote, with no instruction beyond the LED color guide on the remote lanyard.
\end{itemize}

\subsection{Maintainability and Serviceability}

Mall operations staff must be able to maintain a fleet of Smart Carts
with minimal specialist expertise.
\begin{itemize}
  \item The battery pack shall be hot-swappable --- replaceable in under 3 minutes without tools.
  \item All sensor modules shall be individually replaceable without disassembling the main control enclosure.
  \item The system shall log all fault events with timestamps to an onboard SD card for post-session review by technical staff.
  \item Firmware updates shall be deployable over USB without requiring disassembly of the cart.
\end{itemize}

\subsection{Security Requirements}

Although Smart Cart does not handle personal data or payment information,
the remote-to-cart communication channel must be secured to prevent
malicious interference in a busy retail environment.
\begin{itemize}
  \item The UWB pairing between remote and cart shall use a unique session key generated at each power-on, preventing cross-cart interference or hijacking.
  \item No external network connectivity (WiFi, Bluetooth) shall be active during normal operation --- the system is fully self-contained.
  \item Firmware shall only accept signed update packages to prevent unauthorized code execution.
\end{itemize}
